### 2020-03-06 short.body.tex
tweak

The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population \citep{anderson1992infectious}:
\begin{equation}
{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s.
\end{equation}
Then, the \emph{intrinsic} proportion of asymptomatic $z$ and symptomatic $1-z$ transmission is equal to their relative contribution toward the basic reproduction number, 
\begin{eqnarray}
z &=& p {\cal{R}}_a/{\cal{R}}_{0},\\
1-z &=& (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
\end{eqnarray}
Then, the \emph{intrinsic} generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding \emph{intrinsic} generation-interval distributions:
\begin{equation}
g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
\end{equation}
which allows us to express incidence of infection as a renewal process that depends on previous incidence:
\begin{equation}
i(t) = {\cal{R}}_{0} \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
\end{equation}
Yet, this information is not sufficient to disentangle the role of asymptomatic cases, i.e., what fraction of secondary cases can be ascribed to \emph{realized} transmission from asymptomatic cases vs.~symptomatic cases?

>>>>

The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population \citep{anderson1992infectious}:
\begin{equation}
{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s.
\end{equation}
We define the intrinsic proportions of asymptomatic and symptomatic transmission as their relative contribution toward the basic reproduction number:
\begin{eqnarray}
z &=& p {\cal{R}}_a/{\cal{R}}_{0},\\
1-z &=& (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
\end{eqnarray}
Then, the intrinsic generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding intrinsic generation-interval distributions:
\begin{equation}
g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
\end{equation}
which allows us to express incidence of infection as a renewal process that depends on previous incidence:
\begin{equation}
i(t) = {\cal{R}}_{0} \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
\end{equation}
Yet, this information is not sufficient to disentangle the role of asymptomatic cases, i.e., what fraction of secondary cases can be ascribed to \emph{realized} transmission from asymptomatic cases vs.~symptomatic cases?
